\documentclass[18pt]{article}
\title{\textbf{FUTURE OF HEALTH CARE}}
\author{By Harsh Agrawal, 21111021}
\date{}
\begin{document}
\maketitle
\section{\underline{Definition Of Health Care:}}
Health Care is the prevention and treatment of illness or diseases by the help of provided medical expertise and facilities available in current time.
\newline The health care sector, or the medical sector is the most important unit for an individuals life, as we say \textbf{“Being healthy, is being wealthy.”}
\section{\underline{Current Scenario of Health Care:}}
The health care sector is constantly at a growth, newer technologies are coming in use of health sector, people are getting better diagnosis and treatments of diseases. \newline But some problems still occur in this sector and developed technologies must be used in order to get the best out of healthcare.
\section{\underline{The Future Of Health Care:}}
As we know, the health care sector needs to be constantly developing, and so a developed and advanced health care system is the future of human world. As the technology is growing widely, its application to medical use is also increasing. Almost all emerging technologies and methods have some or the other applications in the health care, whether it be diagnosis or treatment.\newline
\textbf{The future of healthcare involves a medical diagnosis and treatment of diseases with all better accuracy, easy to perform methods, and accessible to all individuals.}
\newline The best way to improve the future of health care system is to take in use the technologies, naming some such as \textbf{Artificial Intelligence and Machine Learning(AI-ML), Cloud networks and computing, Information Technology, and many more.} This is the future of health care!!
Taking some Technologies such as \underline{AI-ML} are in further development for many medical devices such as in \textbf{CT Scans, ECGs, Ultrasounds, Dialysis, ventilators, MRIs, and many more.}\newline
\textbf{Cloud computing} is used to store patients’ history and data which are easily accessible to provide better diagnosis.
\newline \textbf{Efficient but low cost Machines} are in development for treatment so that it will be accessible to many financially weak people. 
\newline One of the problem in the health care sector is the \textbf{unreachability of the medical treatments to remote areas and villages.} The future of medical care is inclined to work in this area. \newline Now, \underline{portable machines} and many devices, using the \textbf{Nanotechnology} are under development which will provide easy and accessible treatments to remote and village areas, where there is a lack of medical treatment.
\newline \textbf{Management of large hospitals, which includes staffs, doctors, stocks of devices, medicines, patient records} are an important thing for the health care sector. It is now becoming easier using the technology of \textbf{cloud computing} and networks so that the hospital management will be easy and accurate, \underline{declining the mistakes due to mismanagement and increasing proper treatments. } 
\newline Talking about the medical devices, there is no extent upto which the devices can be developed, as the technology grows, these medical devices will also grow.
We will see the development of \textbf{wearable and portable diagnosis machines, such as wearable ECGs, Handheld Ultrasound machine, Less harmful and small X-rays.}
Treatment devices such as \textbf{Dialysis machines, Ventilators, CPB machines, patient monitors,} and many more are under continuous development. 
Many innovations in the field of \textbf{artificial organs} are under process, using \textbf{tissue technology and nanotechnology.} Artificial Technology are in use to develop the \textbf{robotic hands and legs} with better efficiency and top class features.
\newline Development of a \textbf{Drug dosage system}, for patient under many drugs, is developed \underline{to calculate the accurate amount of drugs required for the body.}
Many less harmful drugs are in use with no side effects. 
\newline \textbf{Future innovations are made in almost all sections of the health care,} \underline{be it the anaesthesia to be used , the hospital beds, or even} \newline \underline{ the medical Insurance provided by companies.}
\newline In the future, surgeries will also be possible through different machines, and doctors can remotely treat the patients through several networking technologies.
\newline \textbf{The future of health care is dynamic}, always under development and innovations, to make the most important sector, most developed and making our lives better, and \textbf{Technology is the key To Future of Health Care.}

\end{document}
